Models

### 2021-08-20 analysis/05_model_metrics.Rmd
Save out useful bits

#get study level slopes for base, and levels for categorical random effect in non-base models
re_slopes <- pmap_dfr(model_df, get_study_slopes)

@@

study_slopes_wide <- study_slopes %>%
  select(study_id, metric, estimate) %>%
  pivot_wider(names_from = "metric", values_from = "estimate")
```

@@

#All model estimates in one dataframe
slope_models <- bind_rows(duration_slope, startyear_slope)

>>>>

#get study level slopes for base, and levels for categorical random effect in non-base models
re_slopes <- pmap_dfr(model_df, get_study_slopes)
pins::pin(re_slopes, board = "github")

@@

# study_slopes_wide <- study_slopes %>%
#   select(study_id, metric, estimate) %>%
#   pivot_wider(names_from = "metric", values_from = "estimate")
```

@@

#All model estimates in one dataframe
slope_models <- bind_rows(duration_slope, startyear_slope)
pins::pin(slope_models, board = "github")
